### 2012-11-25 paper.tex
inserted todo markers

@@

@@

Second run: we use the discretizer with 20 bin.

@@

The attributes are already in a numerical and categorical form, whereby the categories are encoded in an ordinal form. These go from 1 to 4 where 1 is low/bad and 4 is high/good.

\todo{check if ordinal is the correct term when i mean, that the attributes are encoded in numbers, where 1<2, 1<4, 4>2, ...}

\subsection{Desicion Tree}
\subsection{Random Forest}
\subsection{Naive Bayes}
\subsection{Support VectorMachine}

>>>>

\todo{todo marker}

@@

\todo{rewrite this section}

@@

Second run: we use the discretizer with 20 bins.

@@

The values of the data sets's attributes are already in a numerical and categorical form, whereby the categories are encoded in an ordinal form. These go from 1 to 4 where 1 means low/bad and 4 means high/good. This set has no missing values and the attributes do not depend on each other. So we can use the data as is.

\subsection{Desicion Tree}

\todo{todo marker}

\todo{todo marker}

\todo{todo marker}

\subsection{Support VectorMachine}
